Automatic Matching of Bullet Lands

### 2016-05-20 imaging-paper.Rnw
just jittered plot for matches

\begin{figure}[hbtp]
  \centering
<<tree:forest, echo=FALSE, fig.width=5, fig.height=2.5, out.width='.6\\textwidth', warning = FALSE>>=
predm <- melt(bstats, measure.var=c("pred", "forest"))
levels(predm$variable) <- c("Tree", "Forest")
predm$match <- c("KNM", "KM")[as.numeric(predm$match)+1]
qplot(data=predm, value, match, geom="jitter", colour=match, shape=match) + theme_bw() + facet_grid(variable~.) +
    scale_colour_brewer(palette="Paired", labels=c("KNM", "KM")) +
  scale_shape_discrete(labels=c("KNM", "KM")) + ylab("") + 
  xlab("Predicted probability of a match") +
  theme(legend.position="none")

qplot(data=predm, value, geom="boxplot", fill=match, x=match, alpha=I(0.5)) + 
  theme_bw() + facet_grid(variable~.) +
  scale_fill_brewer(palette="Paired", labels=c("KNM", "KM")) +
   ylab("") + 
   xlab("Predicted probability of a match") +
  coord_flip() + 
  theme(legend.position="none")

# qplot(pred, forest, geom="jitter", data=bstats, colour=match, 
#       shape=match) + theme_bw() +
#   theme(legend.position="bottom") +
#   geom_vline(xintercept=0.5, colour="grey50") +
#   geom_hline(yintercept=0.5, colour="grey50") + 
#   xlab("Predictions from decision tree") +
#   ylab("Predictions from random forest")   +
#   scale_colour_brewer(palette="Paired", labels=c("KNM", "KM")) +
#   scale_shape_discrete(labels=c("KNM", "KM"))
# 
@
\caption{\label{fig:tree-forest}Prediction results from the tree and the forest. Using a cut-off probability of 0.5 the forest correctly predicts every single comparison. Compared to the tree, the forest's prediction probabilities are  shrunk towards either end of the prediction range. }
\end{figure}

>>>>

\begin{figure}[hbtp]
  \centering
<<tree:forest, echo=FALSE, fig.width=5, fig.height=2.5, out.width='.6\\textwidth', warning = FALSE>>=
predm <- melt(bstats, measure.var=c("pred", "forest"))
levels(predm$variable) <- c("Tree", "Forest")
predm$match <- c("KNM", "KM")[as.numeric(predm$match)+1]
predm$barrel1 <- gsub("(.*) .*-[0-9]+", "\\1", predm$b1)
predm$barrel2 <- gsub("(.*)-[0-9]+", "\\1", predm$b2)

qplot(data=predm, value, match, geom="jitter", colour=match, shape=match) + theme_bw() + facet_grid(variable~.) +
    scale_colour_brewer(palette="Paired", labels=c("KNM", "KM")) +
  scale_shape_discrete(labels=c("KNM", "KM")) + ylab("") + 
  xlab("Predicted probability of a match") +
  theme(legend.position="none")

@
\caption{\label{fig:tree-forest}Prediction results from the tree and the forest. Using a cut-off probability of 0.5 the forest correctly predicts every single comparison. Compared to the tree, the forest's prediction probabilities are  shrunk towards either end of the prediction range. }
\end{figure}
